Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-06-17 thesis/chapters/ch_introduction.tex
Fixing figure references

The dominant origin of r-process enrichment is highly uncertain, though (as indicated in Figure~\ref{fig:periodic table}) possible channels include NS-NS mergers, neutron star - black hole mergers, neutrino driven winds in core collapse SNe, and exotic SNe, such as magnetic, jet-driven SNe, collapsars, hypernovae, and long-duration gamma-ray bursts \citep[see ][ for recent reviews]{Frebel2018, Cowan2019}. Eu is the most commonly used (and easy to observe) unambiguous observational tracer of r-process enrichment; Ba is also often studied as a tracer, but requires care due to the significant contribution from s-process enrichment. More detailed spectra \citep[e.g.][]{Ji2018a} can trace many more of these elements, which can be used as an important discriminator between nucleosynthetic models.

>>>>

The dominant origin of r-process enrichment is highly uncertain, though (as indicated in Figure~\ref{intro:fig:periodic table}) possible channels include NS-NS mergers, neutron star - black hole mergers, neutrino driven winds in core collapse SNe, and exotic SNe, such as magnetic, jet-driven SNe, collapsars, hypernovae, and long-duration gamma-ray bursts \citep[see ][ for recent reviews]{Frebel2018, Cowan2019}. Eu is the most commonly used (and easy to observe) unambiguous observational tracer of r-process enrichment; Ba is also often studied as a tracer, but requires care due to the significant contribution from s-process enrichment. More detailed spectra \citep[e.g.][]{Ji2018a} can trace many more of these elements, which can be used as an important discriminator between nucleosynthetic models.
